A Linear Solution of the Linearity Challenge

### 2025-12-26 paper/Safety.lagda.tex
global revision

Note the presence of two constructors \AgdaInductiveConstructor{cut-l} and
\AgdaInductiveConstructor{cut-r} which distinguish on whether the hole is found
in the left (respectively, right) sub-context, as per the grammar of reduction
contexts in \Cref{sec:properties}.

@@

>>>>

The constructor \AgdaInductiveConstructor{hole} builds a hole, as the name
implies.
%
The constructors \AgdaInductiveConstructor{cut-l} and
\AgdaInductiveConstructor{cut-r} build reduction contexts where the hole is
found in the left (respectively, right) sub-term of a cut, as per the grammar of
reduction contexts given in \Cref{sec:properties}.

@@

This notion of process substitution preserves typing by construction thanks to
the fact that both processes and reduction contexts are intrinsically typed.
